%  CLA For NVIDIA DIGITS
%  Implemented from CLA file to simplify contribution
%  
%  2017 Sami Kama

\documentclass[a4paper,12pt,notitlepage]{article}
\usepackage[utf8]{inputenc} 
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage[margin=0.75in]{geometry}
\usepackage{hyperref}  % this is needed for forms and links within the text
\setlength{\parindent}{0em}
\setlength{\parskip}{2em}
\hypersetup{ 
  pdftitle    = {Software Grant and Corporate Contributor License Agreement} 
} 
\begin{document}
\pagestyle{empty}
\begin{center}
{\Large The NVIDIA DIGITS\\Software Grant and Corporate Contributor License Agreement ("Agreement")}
\end{center}
Thank you for your interest in the NVIDIA DIGITS Project (the
"Project"). In order to clarify the intellectual property license
granted with Contributions from any person or entity, NVIDIA
Corporation (the “Copyright Holders") must have a Contributor License
Agreement (CLA) on file that has been signed by each Contributor,
indicating agreement to the license terms below. This license is
for your protection as a Contributor as well as the protection of the
Project and its users; it does not change your rights to use your own
Contributions for any other purpose.

This version of the Agreement allows an entity (the "Corporation") to
submit Contributions to the Project, to authorize Contributions
submitted by its designated employees to the Project, and to grant
copyright and patent licenses thereto to the Copyright Holders.

If you have not already done so, please complete and sign, then scan and
email a pdf file of this Agreement to digits@nvidia.com.
Please read this document carefully before signing and keep a copy for
your records.


\begin{Form}
\begin{tabular}{lclcl}
  Corporation name &:&\multicolumn{3}{l}{\TextField[bordercolor=,name=CorporationName,width=10cm,borderwidth=1]{}}\\
  Corporation address &:&\multicolumn{3}{l}{\TextField[bordercolor=,name=CorporationAddr1,width=10cm,borderwidth=1]{}}\\
  & &\multicolumn{3}{l}{\TextField[bordercolor=,name=CorporationAddr2,width=10cm,borderwidth=1]{}}\\
  & &\multicolumn{3}{l}{\TextField[bordercolor=,name=CorporationAddr3,width=10cm,borderwidth=1]{}}\\
  Point of Contact&:&\multicolumn{3}{l}{\TextField[bordercolor=,name=PoC,width=10cm,borderwidth=1]{}}\\
  Email&:&\multicolumn{3}{l}{\TextField[bordercolor=,name=POCemail,width=10cm,borderwidth=1]{}}\\
  Telephone&:&\TextField[bordercolor=,name=POCTel,width=4.5cm,borderwidth=1]{}&Fax:&
  \TextField[bordercolor=,name=POCFax,width=4.5cm,borderwidth=1]{}\\
\end{tabular}

   You accept and agree to the following terms and conditions for Your
   present and future Contributions submitted to the Project. In
   return, the Copyright Holders shall not use Your Contributions in a way
   that is contrary to the public benefit or inconsistent with its nonprofit
   status and bylaws in effect at the time of the Contribution. Except
   for the license granted herein to the Copyright Holders and recipients of
   software distributed by the Copyright Holders, You reserve all right, title,
   and interest in and to Your Contributions.
\begin{enumerate}
\item{ Definitions.

  "You" (or "Your") shall mean the copyright owner or legal entity
  authorized by the copyright owner that is making this Agreement
  with the Copyright Holders. For legal entities, the entity making a
  Contribution and all other entities that control, are controlled by,
  or are under common control with that entity are considered to be a
  single Contributor. For the purposes of this definition, "control"
  means (i) the power, direct or indirect, to cause the direction or
  management of such entity, whether by contract or otherwise, or
  (ii) ownership of fifty percent (50\%) or more of the outstanding
  shares, or (iii) beneficial ownership of such entity.

  "Contribution" shall mean the code, documentation or other original
  works of authorship expressly identified in Schedule B, as well as
  any original work of authorship, including
  any modifications or additions to an existing work, that is intentionally
  submitted by You to the Copyright Holders for inclusion in, or
  documentation of, any of the products owned or managed by the
  Copyright Holders (the "Work"). For the purposes of this definition,
  "submitted" means any form of electronic, verbal, or written
  communication sent to the Copyright Holders or its representatives,
  including but not limited to communication on electronic mailing
  lists, source code control systems, and issue tracking systems
  that are managed by, or on behalf of, the Copyright Holders for the
  purpose of discussing and improving the Work, but excluding
  communication that is conspicuously marked or otherwise designated
  in writing by You as "Not a Contribution."}
\item{Grant of Copyright License. Subject to the terms and conditions
  of this Agreement, You hereby grant to the Copyright Holders and to
  recipients of software distributed by the Copyright Holders a
  perpetual, worldwide, non-exclusive, no-charge, royalty-free,
  irrevocable copyright license to reproduce, prepare derivative works
  of, publicly display, publicly perform, sublicense, and distribute
  Your Contributions and such derivative works.}
\item{Grant of Patent License. Subject to the terms and conditions of
  this Agreement, You hereby grant to the Copyright Holders and to
  recipients of software distributed by the Copyright Holders
  a perpetual, worldwide, non-exclusive, no-charge, royalty-free,
  irrevocable (except as stated in this section) patent license
  to make, have made, use, offer to sell, sell, import, and otherwise
  transfer the Work, where such license applies only to those
  patent claims licensable by You that are necessarily infringed
  by Your Contribution(s) alone or by combination of Your Contribution(s)
  with the Work to which such Contribution(s) were submitted.
  If any entity institutes patent litigation against You or any
  other entity (including a cross-claim or counterclaim in a lawsuit)
  alleging that your Contribution, or the Work to which you have
  contributed, constitutes direct or contributory patent infringement,
  then any patent licenses granted to that entity under this Agreement
  for that Contribution or Work shall terminate as of the date such
  litigation is filed.}
\item{You represent that You are legally entitled to grant the above
  license. You represent further that each employee of the
  Corporation designated on Schedule A below (or in a subsequent
  written modification to that Schedule) is authorized to submit
  Contributions on behalf of the Corporation.}
\item{You represent that each of Your Contributions is Your original
  creation (see section 7 for submissions on behalf of others).}
\item{You are not expected to provide support for Your Contributions,
  except to the extent You desire to provide support. You may provide
  support for free, for a fee, or not at all. Unless required by
  applicable law or agreed to in writing, You provide Your
  Contributions on an "AS IS" BASIS, WITHOUT WARRANTIES OR CONDITIONS
  OF ANY KIND, either express or implied, including, without
  limitation, any warranties or conditions of TITLE, NON-INFRINGEMENT,
  MERCHANTABILITY, or FITNESS FOR A PARTICULAR PURPOSE}
\item{Should You wish to submit work that is not Your original creation,
  You may submit it to the Copyright Holders separately from any
  Contribution, identifying the complete details of its source and
  of any license or other restriction (including, but not limited
  to, related patents, trademarks, and license agreements) of which
  you are personally aware, and conspicuously marking the work as
  "Submitted on behalf of a third-party: [named here]"}
\item{It is your responsibility to notify the Copyright Holders when any change
  is required to the list of designated employees authorized to submit
  Contributions on behalf of the Corporation, or to the Corporation's
  Point of Contact with the Copyright Holders.}
\end{enumerate}
%\vskip 2cm
\begin{tabular}{lclcl}
  Please sign &:&\TextField[bordercolor=,name=Signature,width=6cm,borderwidth=1]{}&Date:&
  \TextField[bordercolor=,name=SignDate,width=3cm,borderwidth=1]{}\\
  Title &:&\multicolumn{3}{l}{\TextField[bordercolor=,name=SignerTitle,width=10cm,borderwidth=1]{}}\\
  Corporation&:&\multicolumn{3}{l}{\TextField[bordercolor=,name=SignerCorp,width=10cm,borderwidth=1]{}}\\
\end{tabular}

Schedule A

   [Initial list of designated employees.  NB: authorization is not
    tied to particular Contributions.]
\vskip 3cm

Schedule B

   [Identification of optional concurrent software grant.  Would be
    left blank or omitted if there is no concurrent software grant.]

\hfill ~\\
\end{Form}

\end{document}
